%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% use \cvblock command for Experience
% Arguments:
%   #1: [Optional] Bullet points (\item statements)
%   #2: Institution/Organization name
%   #3: Location (city, state/country)
%   #4: Position title or degree
%   #5: Date range

\section*{Experience}

\cvblock[
    \item Synthesized papers around LLMs and AI Agents using prompt engineering for filtering to classify them into two categories; relevant and not relevant based on their title and abstract and manually evaluated 30\% of the papers with 99\% accuracy, with all errors being false negatives using open source models.
    \item Performed experiment and reverse engineering of LLM360 models to understand the underlying mechanisms of LLMs.
]{ResolutionAI}{Accra, Ghana}{Pre-doctoral Researcher}{May-Aug,2025}
\medskip

\cvblock[
    \item Involved in bilingual alignment multi-turn datasets curation for supervised fine-tuning and direct preference optimization to improve EXAONE 3.0 instruction following ability and align to human preferences and ethics.
    \item Collabrated with team members to craft question-answer datasets with its corresponding ”Pass” or “Fail” annotation, designed to cover a wide range of unethical and insecure scenarios including hate, bias, illegal content, information hazards such as the use of private data in training for the evaluation of EXAONE 3.0 7.8B instruction-tuned model where the model produces appropriate responses 84\% of the time when faced with carefully curated adversarial queries.
]{LG AI Research, collabration with DataMaker}{Accra, Ghana}{Research Assistant}{Aug,2023-Aug,2024}

\medskip
\cvblock[
    \item Spearheaded the end-to-end development of an AI-powered agritech solution, ”Real Time Automatic Detection of Mosaic Virus in Crops,” specifically designed to mitigate crop loss across high-value horticultural sectors including tomatoes, peppers, and beans.
    \item Architected the project’s technical roadmap by selecting and implementing a Convolutional Neural Network (CNN) architecture, leveraging Microsoft Azure GPU cloud infrastructure for high-performance model training.
    \item Conducted rigorous real-time field testing using OAK-D spatial AI cameras to ensure the product met user-centered requirements for speed and accuracy in diverse environmental conditions.
]{TexkLab}{Cape Coast, Ghana}{Machine Learning Engineer}{Jan,2021-Dec,2023}

\medskip
\cvblock[
    \item Developed Excel-based financial models that improved the accuracy of revenue and expenditure predictions by 25\%, reducing the need for mid-year supplementary budget adjustments.
    \item Involved in the drafting and implementation of the Fee-Fixing Resolution, resulting in an IGF performance that exceeded the annual budget by over 3\% through optimized rate and license collection.
    \item Conducted in-depth variance analysis for major infrastructure projects, identifying 15\% in potential cost savings by reallocating underutilized funds to high-priority sanitation and education initiatives.
]{Ministry of Local Government and Rural Development}{Accra, Ghana}{Data Analyst}{Aug,2019-Dec,2020}
